### 2014-02-25 paper/retrofit.tex
More text
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie
io   ::=  (il, id ie)
Q    ::=  nil | io , Q

CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
\end{code}

\begin{mathpar}
%   \and
%   \inferrule[I-done]
%   {|
%   |}
%   {|
%   iconf iS (fullconf id il tS iv, ldots)
%   .->
%   iS ; sched done (fullconf id il tS iv, ldots)
%   |}

@@

\inferrule[I-labelOp]
{ |denot (il1 lop il2) = iv|}
{ |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }
\end{mathpar}
\caption{IFC language}
\label{fig:ifc}
\end{figure}

@@

\begin{code}
ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)

conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
\end{code}

@@

@@

\and
\inferrule[T-border]
{ } {| conf tS (TI (IT (te))) -> conf tS te|}
\end{mathpar}
\caption{The embedding}
\label{fig:embedding-grammar}
\end{figure}

@@

The filter function |filter il Q| removes message whose labels do not
flow to |il|. Specifically, if |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|; otherwise:
\[
|filter il ((il', id, ie) , Q )| = \left\{
\begin{array}{l l}
|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]

In the case of extending
\begin{mathpar}
\inferrule[I-bool]
{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
\and
\inferrule[T-bool]
{ |b member {true, false}| } {| intE (TI b) -> intE b |}
\end{mathpar}

>>>>

Next, we describe the IFC language.  \Red{Description of the IFC language as
a standard floating label system, or backwards reference to the
background section.}  In Figure~\ref{fig:ifc}, we describe the syntax
of the language, and provide rules for all operations which operate on a single
thread.  \Red{One could imagine these rules giving the definition of a very
boring information flow control language, by defining |niconf iS id il ie| appropriately
and providing an appropriate erasure function.}

We use the notation |filter il Q| to indicate a filter function which removes message whose labels do not
flow to |il|. Specifically, if |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|; otherwise:
\[
|filter il ((il', id, ie) , Q )| = \left\{
\begin{array}{l l}
|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie
io   ::=  (il, id ie)
Q    ::=  nil | io , Q
\end{code}

@@

\inferrule[I-labelOp]
{ |denot (il1 lop il2) = iv|}
{ |niconf iS id il (il1 lop il2) -> niconf iS id il iv| }
\end{mathpar}
\caption{IFC language, single-thread operations}
\label{fig:ifc}
\end{figure}

Finally, in Figure~\ref{fig:embedding},
we provide all of the rules responsible for actually carrying out the embedding:

\begin{itemize}
    \item We extend the values, expressions and evaluation contexts of both languages to allow for embeddings terms in one language to be embedded in the other.  \Red{For now, we defer discussion on how these boundaries mediate between the type systems of the two languages.}
    \item We reinterpret |CE| to be evaluation contexts on threadpools.  By assumption, only the first thread in the threadpool executes.
    \item We define |->|, operation on a single thread, in terms of |.->|, operation on thread pools.  The correspondence is simple: a thread executes a step, and then is rescheduled in the thread pool according to schedule policy $\alpha$. \Red{More on schedule policies later}
    \item Finally, we define some rules for scheduling, handling forking threads (which interact with the state of the target language) and intermediating between the borders of the two languages. \Red{As written, these rules will not preserve type-safety of the underyling language, but it is easy to adjust them to ensure they do so.}
\end{itemize}

The fork rule is of particular interest; it is defined in terms of a function $\kappa$.
Conservatively, $\kappa$ may be simply thought of as the identity function, in which
case the semantics of fork are such that the state of the target language is \emph{cloned}
when forking occurs.  However, this is not necessary: it is also valid for $\kappa$
to remove entries from the state.  \Red{For more information about when this is not the
fork semantics you want, see the concrete implementation section.}

@@

\begin{code}
ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
CE[e] -> iconf iS (it, ldots) @= CE[e] .-> iconf iS (sched step (it, ldots))
\end{code}

@@

\and
\inferrule[I-done]
{|
|}
{|
iconf iS (fullconf id il tS iv, ldots)
.->
iS ; sched done (fullconf id il tS iv, ldots)
|}

@@

\and
\inferrule[T-border]
{ } {| conf tS (TI (IT (te))) -> conf tS te|}
\end{mathpar}
\caption{The embedding}
\label{fig:embedding}
\end{figure}

@@

\Red{When both languages have booleans, it is relatively simple to define
a natural embedding which preserves booleans across boundaries.}
\begin{mathpar}
\inferrule[I-bool]
{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
\and
\inferrule[T-bool]
{ |b member {true, false}| } {| intE (TI b) -> intE b |}
\end{mathpar}
